---
title: "Peer-graded Assignment: R Markdown Presentation & Plotly"
author: "Bruno"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

## The airquality dataset

The *airquality* dataset contains daily air quality measurements in New York from May to September, 1973. 

We are interested in the relationship of the following variables according to different months:

- **Ozone:** Mean ozone in parts per billion from 13:00 to 15:00 hours at Roosevelt Island,

- **Solar.R:** Solar radiation in Langleys in the frequency band 4000–7700 Angstroms from 08:00 to 12:00 hours at Central Park,

- **Temp:** Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.

## Data preview

```{r, fig.align = 'center'}
df <- airquality
df$Month <- factor(month.name[df$Month], levels = c("May", "June", "July", "August", "September"))

head(df, n = 15)
```

## Output

```{r}
library(plotly)

fig <- plot_ly(df, x = ~Ozone, y = ~Solar.R, z = ~Temp, color = ~Month) 

fig
```


